% resume.tex
%
% Layout (c) 2007-2011 Jeremy B. R. Edberg <jedberg@gmail.com> http://www.jedberg.net
%

% general setup
\documentclass[12pt]{article}
\usepackage{enumitem}			% for itemize
\usepackage{setspace}				% for setstretch
\usepackage{geometry} 			% for geometry
\usepackage{verbatim}				% for multi-line comments
\usepackage{hyperref}
\geometry{letterpaper, twoside}		% sets paper settings (can also be a4paper)
\setstretch{0.75}						% adjusts spacing of entire document
\pagestyle{empty}						% sets page style
\setlength{\tabcolsep}{0in}		% the space between columns
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    }

% section setup
\newcommand\posthline{1.5mm}		% the space between an hline and the next line
\newcommand\sectionspacing{3mm}	% the space between sections (e.g. UCSD->AMHS, AMHS-> Experience)

% list setup
\newcommand\topsepsize{5pt}			% the space before and after an itemized list
\newcommand\listleftmargin{5mm}	% the left margin of the list items
\newcommand\listlabelsep{2.5mm}	% the space between the bullet and text of a list item
\newcommand\listitemsep{-1.5mm}	% the space between the list items
\newcommand\listbullet{\raisebox{0.25ex}{$\bullet$}}				% the size of the bullet, height-centered normal
%\newcommand\listbullet{\raisebox{0.35ex}{\tiny$\bullet$}}		% the size of the bullet, height-centered tiny

% margin setup
\oddsidemargin  -0.4in
\evensidemargin -0.4in
\textwidth      7.3in
\headheight    -1.05in
\topmargin      0.15in
%\topmargin      -0.85in
\textheight=10.7in

\begin{document}

% commenting out sections
\begin{comment}
...
\end{comment}

% header
\begin{center}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr}
&\huge{\textbf{\sc{Sumeet Bansal}}}&\\
LinkedIn: s-bansal & Email: sumeetbansal@gmail.com & Cell: (408) 250-3097\\
\hline\hline
\end{tabular*}
\end{center}

% Education
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large{\sc{Education}}\\
\hline
\end{tabular*}

%% UC San Diego (UCSD)
\vspace{\posthline}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{University of California, San Diego} & La Jolla, CA \\
\emph{B.S., Computer Science; Minor in Mathematics.} & \emph{Graduated March 2020}
\end{tabular*}
\begin{comment}
{\small Provost Honors. Relevant Coursework:}
\vspace{1mm}		% one-time for spacing out relevant coursework

\small
\noindent
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llll}
CSE 100 & \footnotesize Advanced Data Structures
&
CSE 101 & \footnotesize Design and Analysis of Algorithms
\\
CSE 158 & \footnotesize Recommender Systems and Web Mining
&
CSE 170 & \footnotesize Interaction Design
\\
ECE 140 & \footnotesize The Art of Product Engineering
&
MATH 189 & \footnotesize Exploratory Data Analysis and Inference
\\
\end{tabular*}
\end{comment}

%% Archbishop Mitty (AMHS)
\begin{comment}
\vspace{\sectionspacing}
\noindent
\normalsize 		% necessary because tabular previously set to \small for rel. coursework
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Archbishop Mitty High School} & San Jose, CA \\
\emph{Graduated with Honors} & \emph{August 2012 to May 2016}
\end{tabular*}
{\small\noindent
GPA: 4.14. SAT: 2260. Awards: 2013 FIRST Robotics Competition CalGames System Design Award, 2015 FIRST Robotics Competition CalGames System Design Award.
}
\end{comment}

%% Skills
\vspace{\sectionspacing}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large{\sc{Skills \& Qualifications}}\\
\hline
\end{tabular*}

\vspace{\posthline}
	\noindent\textbf{Languages} -- Java, Python, SQL, TypeScript/JavaScript, Rust, Shell\\
	\noindent\textbf{Technologies/Frameworks} -- CI/CD, Docker, Node, React, Cassandra

% Experience
\vspace{\sectionspacing}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large{\sc{Experience}}\\
\hline
\end{tabular*}

%% Moxie
\vspace{\posthline}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Moxie} & New York, NY \\
\emph{Software Engineer, Co-founder} & \emph{March 2024 to Present} \\
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Raised a seed round led by Village Global and filled out by angel investors.
        \item Built, deployed, and maintained the entire backend for the product, an app store and hosted user management solution tailored to less technical app developers enabled by lowered barriers to entry, using TypeScript, Postgres, and the Stripe and Auth0 APIs.
        \item Experimented with different customer profiles and iterated on the product based on feedback from users and design partners.
\end{itemize}

%% Palantir
\vspace{\sectionspacing}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Palantir} & New York, NY \\
\emph{Software Engineer} & \emph{May 2020 to September 2023} \\
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Developed the \href{https://www.palantir.com/docs/foundry/time-series/time-series-overview}{time series} product, which ingests large datasets (up to tens of Terabytes each) containing millions of unique time series and enables users to execute complex queries composed of transforms and aggregations against those time series within seconds.
	\item The product supports business-critical workflows at global institutions like oil-and-gas supermajors, automotive and aerospace manufacturers, and national health agencies. For example, Airbus instruments its aircraft with thousands of sensors recording measurements at millisecond frequency, for every flight, across their fleet, and uses our time series product to manage that volume of sensor data and plan preventative aircraft maintenance. Clients frequently use time series to monitor the health of their assets in real-time, e.g. British Petroleum and its energy platforms, several national health agencies and their COVID responses.
	\item I worked extensively across the product stack: multiple Java services, a Rust service, a Python library, and a Typescript/React front-end.
	\item Owned streaming workflows for time series, a functionality highly-demanded from current and prospective customers. The architecture for streaming workflows barely existed as a skeleton; I shipped tens of thousands of lines of code to production, wrote documentation, added monitoring and alerting, collaborated with early adopters to iron out issues and address pain points, released the feature, and enabled our largest customer to migrate from their custom streaming solution. As clients scaled their streaming usage, I profiled and analyzed runtime to improve stability (e.g. memory usage) and optimize performance.
	\item Enabled usage-based pricing for time series and unlocked millions of dollars in new contract value by implementing compute reporting for time series services and updating all significant time series clients in the Foundry platform one-by-one to pass along compute attribution to time series.
	\item Reduced cloud costs by several hundred thousand dollars annually by building the next-generation of time series architecture, which would be more tightly integrated with the Foundry platform and write orders of magnitude less metadata, eliminating the need for dedicated Cassandra clusters on hundreds of customer deployments.
	\item Contributed to the support rotation, where I responded to pages and investigated and fixed time series issues in the field, such as security vulnerabilities, product bugs, configuration errors, performance issues, and complex system failures. I closed over 1000 pages. While on support, I was responsible for maintaining strict SLAs across dozens of customer deployments.
\end{itemize}

%% Palantir
\vspace{\posthline}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Palantir} & New York, NY \\
\emph{Software Engineer Intern} & \emph{June 2019 to September 2019} \\
\end{tabular*}
\begin{comment}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Worked on a a permissioned registry service to store user-authored code called \href{https://www.palantir.com/docs/foundry/functions/overview/}{Functions}, and Function metadata and specifications (e.g. input/output data types, documentation, location of Function code). Designed and implemented a search API for published Functions in Java using Cassandra and Elasticsearch.
	\item Developed a custom TypeScript logger conforming to the internal service specification, e.g. integration with internal authentication service, tracing by Function execution context, support for log rotation.
\end{itemize}
\end{comment}

%% IBM Watson Health
\vspace{\sectionspacing}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{IBM Watson Health} & Milwaukee, WI \\
\emph{Software Developer Intern} & \emph{June 2018 to September 2018} \\
\end{tabular*}
\begin{comment}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Reworked continuous integration system to include automated remote unit testing and brought test harness up to federal standards.
	\item Developed a data integrity project to ensure patient data isn't being mutated by the program.
	\item Developed a data transformation tool for patient data to fix a critical compatibility issue in production.
	\item Designed a proof-of-concept blockchain with the premise of smart contracts for pharmaceutical prescriptions.
\end{itemize}
\end{comment}

%% Actiance
\vspace{\sectionspacing}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Actiance} & Redwood City, CA \\
\emph{Engineering R\&D %and Product Management
Intern} & \emph{June 2017 to September 2017} \\
\end{tabular*}
\begin{comment}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
%	\item Verified QA testing for the Rhine release of the Alcatraz platform.
	\item Led a team of three interns in developing an independent anomaly detection project written in Java.
	\item Developed and shipped a diagnostic service that's currently used in production to significantly shorten development and deployment cycles by ensuring parity across multiple product sites' server configurations.
%	\item Automated processes for generating data stores of entire product sites' server configurations.
	\item Created a flexible MongoDB-based query engine that generates detailed statistical server analyses via a command line interface and later migrated the entire project to a fully functional SQL-based implementation.
	\item Extended the tool into a REST API using Spring Boot and built an online dashboard using Angular.
%	\item Oversaw company-wide deployment and adoption across different teams, domestic and international (e.g. Engineering, Network Operations, QA).
	\item Presented well-received demos to many senior executives, including the CEO. % Incorporated feedback and added requested functionality for specific use cases.
%	\item Worked with Program Management to migrate programs to the BigPicture application for improved risk assessment, swim lane progress updates and milestone planning.
\end{itemize}
\end{comment}

%% Zscaler
\vspace{\sectionspacing}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Zscaler} & San Jose, CA \\
\emph{Emerging Technologies Intern} & \emph{June 2015 to August 2015} \\
\end{tabular*}
\begin{comment}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Classified and prioritized global cyberthreats from incoming production server data streams.
	\item Projected the parsed cyberthreat data onto a real-time web visualization using the Google Maps API.
\end{itemize}
\end{comment}

\begin{comment}
%% Projects
\vspace{\sectionspacing}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large{\sc{Projects}}\\
\hline
\end{tabular*}

%% last.fm explorer
\vspace{\posthline}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Last.fm Spelunker} & \textit{https://git.io/vd0WS}\\
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Generates an exhaustive SQL database of users' listening histories and related info through the Last.fm API.
	\item Identifies historical patterns in listening habits, e.g. seasonal preferences for artists or genres.
	\item Graphs listening statistics and long-term trends with streamgraphs and connections between related artists with hierarchical edge bundles using Python, Flask, and the D3.js data visualization library.
\end{itemize}

%% Triton Scheduler
\vspace{\sectionspacing}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Triton Scheduler} & \textit{https://git.io/vd0WQ}\\
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item A Chrome extension to easily populate Google Calendars with academic schedule for the quarter.
	\item Uses web scraping to parse and clean schedule data from the online WebReg class registration tool.
	\item Handles the user authentication and authorization process through the OAuth 2.0 protocol.
	\item Adds all academic events from the registration tool to Google Calendar via the Google Calendar API.
\end{itemize}

%% Extracurriculars
\vspace{\sectionspacing}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large{\sc{Extracurriculars}}\\
\hline
\end{tabular*}

%% SEDS
\vspace{\posthline}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Students for the Exploration and Development of Space (SEDS)} & La Jolla, CA \\
\emph{Webmaster} & \emph{January 2018 to Present}
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Responsible for the design and maintenance of the organization's website (sedsucsd.org) and internal member portal.
	\item Integrated a conference registration and management system with the site to manage a conference with an attendance of several hundred.
\end{itemize}
\vspace{\posthline}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\emph{Software Developer} & \emph{September 2017 to March 2018}
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Member of the data acquisition team on the Colossus project, a NASA-funded static fire test stand having a net worth of \$330,000.
	\item Automated the sequence of actions required to obtain reliable thrust readings, designed a highly-redudant system with numerous background and safety checks, and developed data loggers, a dedicated analytics platform, and a responsive web interface to enable real-time monitoring of the Colossus system.
\end{itemize}

%% TSE
\vspace{\sectionspacing}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Triton Software Engineering} & San Diego, CA \\
\emph{President} & \emph{May 2018 to Present}
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Managed logistics, rebranded and defined the vision, and created growth and media strategies for an interdisciplinary 40-person student org that designs and develops pro-bono technology resources, typically web and mobile applications, for social good.
	\item Established partnerships with local non-profits, social enterprise venture firms, and industry professionals.
	\item Pushed the adoption of industry-standard development practices (proper Git workflows with code reviews, CI/CD and tooling, style guides, etc.) and a more multidisciplinary development approach with a greater emphasis on human-centered design.
	\item Established a scalable tech infrastructure using AWS and a system for regular management and technical check-ins with individual teams.
	\item Gathered specifications for, architected, and worked on multiple projects ranging from a geographic data infrastructure for a nationally distributed network of food sources and food banks to an electronic patient records system for medical clinics in low-resource areas of Tijuana and Guadalajara.
\end{itemize}
\vspace{\posthline}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\emph{Project Manager} & \emph{January 2018 to June 2018}
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Led a team of student developers in implementing projects for social good; followed Agile methodology.
%	\item Created a structured lesson plan to teach team members web development with the MEAN stack.
%	\item Developed a medical records system for a pop-up health clinic program in low-resource areas (e.g. Tijuana).
%	\item Created a market evaluation tool for community stakeholders and ethnic grocers to improve the urban food environment in San Diego.
\end{itemize}

%% FRC
\vspace{\sectionspacing}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{FRC Team 1351 -- TKO} & San Jose, CA \\
\emph{Mentor, former Project Lead} & \emph{September 2012 to Present}
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Provided input on robot design, overall team strategy, and software design.
	\item Participated in design reviews for various robot subsystems and post-competition SWOT analysis.
	\item While a project lead, managed several team members, had complete autonomy in designing multiple vital subsystems, and had significant input on high-level design and strategy as a core member.
\end{itemize}

%% RAFT
\vspace{\sectionspacing}
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Resource Area for Teachers} & San Jose, CA \\
\emph{Volunteer} & \emph{August 2010 to May 2016}
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Created low-budget school projects for teachers to use in classrooms to demonstrate scientific principles.
	\item Handled accepting and sorting donations.
	\item Organized the Back to School summer sale.
\end{itemize}

%% RANA
\vspace{\sectionspacing}
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{Rajasthan Association of North America} & San Jose, CA \\
	\emph{Youth Director} & \emph{February 2015 to February 2016}
\end{tabular*}
\begin{itemize}[leftmargin=\listleftmargin, labelsep=\listlabelsep, itemsep=\listitemsep, label=\listbullet, topsep=\topsepsize]
	\small
	\item Served on the Executive Committee and helped organize community outreach and events.
	\item Developed an online system to easily add people to the organization's mailing list during the most-attended event of the year. Contributed code to the website for content and appearance.
\end{itemize}
\end{comment}

\end{document}